%-------------------------
% Rover Resume - Fancy Template
% Link: https://github.com/subidit/rover-resume
%------------------------

\documentclass[10pt]{article}

\usepackage[T1]{fontenc}
\usepackage{inter} % https://tug.org/FontCatalogue/
\renewcommand*\familydefault{\sfdefault}

\usepackage{geometry}
\geometry{
a4paper,
top=1in,
bottom=1in,
left=1in,
right=1in
}

\setcounter{secnumdepth}{0} % remove section numbering
\pdfgentounicode=1 % make ATS friendly

\usepackage{enumitem}
\setlist[itemize]{
    noitemsep,
    left=0pt..1.5em
}
\setlist[description]{itemsep=0pt}
\setlist[enumerate]{align=left, noitemsep}

\usepackage[dvipsnames]{xcolor}
% \usepackage[dvipsnames, svgnames, x11names]{xcolor} 
% \usepackage[dvipsnames]{xcolor} % xcolor.pdf Sec.4 Colors by Name
\colorlet{icnclr}{gray}
% \colorlet [⟨type⟩]{⟨name⟩}[⟨num model⟩]{⟨color ⟩}
% \definecolor[⟨type⟩]{⟨name⟩}{⟨model-list⟩}{⟨spec-list⟩}


\usepackage{titlesec}
% \titlespacing{command}{left spacing}{before spacing}{after spacing}[right]
% \titlespacing{\section}{0pt}{*3}{*1}
\titlespacing{\subsection}{0pt}{*0}{*0}
\titlespacing{\subsubsection}{0pt}{*0}{*0}
% \titleformat{<command>}[<shape>]{<format>}{<label>}{<sec>}{<before-code>}[<after-code>]  
\titleformat{\section}{\color{Sepia}\large\fontseries{black}\selectfont\uppercase}{}{}{\ruleafter}[\global\RemVStrue]
\titleformat{\subsection}{\large\fontseries{semibold}\selectfont}{}{}{\rvs}
\titleformat{\subsubsection}{\large\fontseries{medium}\selectfont}{}{}{}

\usepackage{xhfill} 
\newcommand\ruleafter[1]{#1~\xrfill[.5ex]{1pt}[gray]} % add rule after title in .5 x-height 

\newif\ifRemVS % remove vspace between \section & \subsection
\newcommand{\rvs}{
    \ifRemVS
        \vspace{-1.5ex}
    \fi
    \global\RemVSfalse
}


\usepackage{fontawesome5}

\usepackage[bookmarks=false]{hyperref} % [imp!]
\hypersetup{ 
    colorlinks=true,
    urlcolor=Sepia,
    pdftitle={Colby Noel Resume},
}

\usepackage[page]{totalcount}
\usepackage{fancyhdr}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}	
\fancyhf{}							
\cfoot{\color{darkgray} Colby Noel's Resume -- Page \thepage{} of \totalpages}


\begin{document}

%== HEADER ==%
\begin{center}
    {\fontsize{30}{30}\selectfont\interthin COLBY\interheavy NOEL} \\ \bigskip
    {\color{icnclr}\faEnvelope[regular]} \href{mailto:colbynoel02@gmail.com}{colbynoel02@gmail.com} 
    $|$ 
    {\color{icnclr}\faIcon{mobile-alt}} \href{tel:8704505622}{(870)450-5622}
    $|$ 
    {\color{icnclr}\faLinkedinIn} \href{https://www.linkedin.com/in/colby-noel-a56365208/}{linkedin.com/colby-noel} 
    $|$ 
    {\color{icnclr}\faGithub} \href{https://github.com/colbynoel}{colbynoel}
\end{center}

\section{Experience}
%===================
\subsection{Gainwell Technologies LLC \hfill May 2022 -- Present}
\subsubsection{Associate Software Developer \hfill Conway, AR}
\begin{itemize}

    % \item Designed and Developed a {micro-service RESTful API for dental imagery, serving as an intermediary between four dental clearinghouses. Integrated JWT authentication, image cacheing, and deployment was conducted with AWS EKS, Argo CD, and GitHub Actions. This application resulted in a 98.3\% execution time save for the adjudicators while also boasting \textbf{150+} users at any given time. With rolling updates to ensure minimal downtime between application versions.
    \item Designed and engineered a micro-service RESTful API for dental imagery, that resulted in a 98.3\% reduced execution time while also boasting 150+ adjudicators at any given time. 
    \\ % New Line
    % \item Developed a comprehensive data extraction and analysis system using the \textbf{Pandas Data Analysis Library}, integrating Microsoft Graph and ZScaler data for remote absenteeism tracking and physical location use assessment for over \textbf{8,000+ employees}. Efficiency was optimized through the use of \textbf{async/await requests}, with tasks containerized using \textbf{Docker} for granular service management, and \textbf{Apache Airflow} utilized for scheduling and logging.
    \item Developed a comprehensive data extraction and analysis system, integrating Microsoft Graph and Zscaler data for remote absenteeism tracking and physical location use assessment for over 8,000+ employees and contractors.
    \\ % New Line
    \item Engineered an automated documentation pipeline using GitHub Actions and MkDocs, enabling real-time updates on GitHub Pages and AWS. Introduced a system for automated conversions of Word, Email, and PDF content into Markdown, thereby streamlining the integration of diverse content.
\end{itemize}

\subsection{Flower Shop Network \hfill May 2021 - August 2021}
\subsubsection{Full Stack Developer Intern \hfill Paragould, AR}
\begin{itemize}
    \item Proactively maintained system reliability by regularly auditing error logs to reduce critical issues, which spearheaded a seamless transition from PHP 5.3 to PHP 7 ensuring up-to-date language use.
    \\ % New Line
    \item Developed a comprehensive internal web report to manage client domain renewals, activities, and associated costs, significantly enhancing operational efficiency and domain management for the division.
\end{itemize}

\section{Education}
%==============
\subsection{University of Central Arkansas $|$ {\normalfont\textit{Bachelors of Computer Science}} \hfill May 2023}
\begin{itemize}
    \item Cumulative GPA: 3.798
\end{itemize}

\section{Skills}
%===============
\begin{description}
    \item[Programming Languages] Python, C++, Javascript, C\#, Java, Terraform 
    \item[Cloud Technologies] AWS: S3, EC2, CloudFront, CloudWatch, Lambda, Glue, ECR, EKS
    \item[Tools] Kubernetes, Apache Airflow, Grafana, Hashicorp Vault, Postman
\end{description}

\section{Leadership}
%===============================
\begin{enumerate}[itemsep=0pt]
  \item [\textbf{Computer Science Club President -- \textit{2022/2023:}}] Spearheaded a thriving and collaborative environment for computer science majors, fostering a culture of sharing and learning. Launched a competitive programming team, enabling club participation in various tournaments, and increased club participation by 10x.
  \item [\textbf{Robotics Club Co-Founder/Vice-President -- \textit{2020/2023:}}] Co-established and promoted the Robotics club on campus, playing a key role in developing its vision and future initiatives. Lead strategic planning and student outreach efforts, aimed at increasing club participation and fostering a robust robotics community.
\item [\textbf{Intern Mentor -- \textit{Summer 2023:}}] Successfully managed and mentored a class of interns. Oversaw the progress and development of three assigned interns, each working on individual projects that cultivated their technical abilities and client communication skills.
\end{enumerate}

\end{document}